---
title: "Demo of dsBayesPathAnalysis's 'ds.hessSEM' with SYNTH data of Proof-of-Concept (0.3.0)"
output:
  pdf_document: default
  rmarkdown::html_vignette: default
vignette: |
  %\VignetteIndexEntry{Demo of dsBayesPathAnalysis's 'ds.hessSEM' with SYNTH data of Proof-of-Concept (0.3.0)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

A demonstration of dsBayesPathAnalysis's 'ds.hessSEM' with SYNTH data of Proof-of-Concept (0.3.0)

### Requirements

##### Client-side
- Opal 4.3.1 (service)
- Rock 1.0.12 (service)
- DSOpal 1.3.1 (R Package)
- DSI 1.3.0 (R Package)
- dsBayesPathAnalysisClient 0.3.0 (R Package)

##### Server-side
- dsBayesPathAnalysis 0.3.0 (R Package)
- rBSEM 0.2.2 (R Package)

### Load packages
```{r}
library("DSOpal")
library("DSI")
library("dsBaseClient")
library("dsBayesPathAnalysisClient")
```
### Log into Opal
```{r}
builder <- DSI::newDSLoginBuilder(.silent = TRUE)
builder$append(server = "sem", url = "https://192.168.56.100:8443/", user = "administrator", password = "datashield_test&", resource = "SEM.sem_data")
login.data <- builder$build()

conns <- DSI::datashield.login(logins = login.data, assign = TRUE, symbol = "R", opts = getOption("datashield.opts", list(ssl_verifyhost=0, ssl_verifypeer=0)))
```
### Setup server-side variables needed
```{r}
# list(c(1:10), c(11:20), c(21:40), c(41:50), c(51:60), c(61))
ds.assign(toAssign = "c(1,2,3,4,5,6,7,8,9,10)", newobj = "blockList_1")
ds.assign(toAssign = "c(11,12,13,14,15,16,17,18,19,20)", newobj = "blockList_2")
ds.assign(toAssign = "c(21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40)", newobj = "blockList_3")
ds.assign(toAssign = "c(41,42,43,44,45,46,47,48,49,50)", newobj = "blockList_4")
ds.assign(toAssign = "c(51,52,53,54,55,56,57,58,59,60)", newobj = "blockList_5")
ds.assign(toAssign = "c(61)", newobj = "blockList_6")
ds.list(c("blockList_1", "blockList_2", "blockList_3", "blockList_4", "blockList_5", "blockList_6"), newobj = "blockList")

# NULL
ds.assign(toAssign="NULL", newobj = "varType")

# matrix(c(0,1,1,0,0,0,0,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0,1,0,0,0,0,0,0,1,0,0,0,0,0,0), byrow=TRUE, ncol=6, nrow=6)
ds.matrix(mdata = c(0,1,1,0,0,0,0,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0,1,0,0,0,0,0,0,1,0,0,0,0,0,0), byrow = TRUE, nrows.scalar = 6, ncols.scalar = 6, newobj = "SEMGraph")
```
### Invoke 'ds.hessSEM' with sem_data.txt
```{r}
sem_data.results <- dsBayesPathAnalysisClient::ds.hessSEM("R", "synth_data.txt", "blockList", "varType", "SEMGraph", TRUE, "S", 10000, 1000, 1, 0, 1)
```
### Output and save results for sem_data.txt
```{r}
print(sem_data.results)
save(sem_data.results, file="synth_data.results.Rd")
```
### Log out of Opal
```{r}
DSI::datashield.logout(conns)
```