---
output:
  pdf_document: default
  html_document: default
---
# Demo

---
title: "Demo of dsBayesPathAnalysis's 'ds.hessSEM' of Proof-of-Concept (0.1.1)"
output: html_notebook
---

A demonstration of dsBayesPathAnalysis's 'ds.hessSEM' of Proof-of-Concept (0.1.1)"

### Requirements
- Opal 4.2.1 (service)
- DSOpal 1.3.0 (R Package)
- DSI 1.3.0 (R Package)
- dsBayesPathAnalysisClient 0.1.1 (R Package)

- dsBayesPathAnalysis 0.1.1 (R Package)
- rBSEM 1.2.2 (R Package)

### Load packages
```{r}
library(DSOpal)
library(DSI)
library(dsBayesPathAnalysisClient)
```
### Log into Opal
```{r}
builder <- DSI::newDSLoginBuilder(.silent = TRUE)
builder$append(server = "sem", url = "http://192.168.56.100:8080/", user = "administrator", password = "datashield_test&", resource = "SEM.sem_data")
login.data <- builder$build()

conns <- DSI::datashield.login(logins = login.data, assign = TRUE, symbol = "R")
```
### Invoke 'ds.hessSEM' with sem_data.txt
```{r}
res <- dsBayesPathAnalysisClient::ds.hessSEM("R", "sem_data.txt", 200, 1, 0, 1)
```
### Output results for sem_data.txt
```{r}
print(res)
```
### Invoke 'ds.hessSEM' with na_sem_data.txt
```{r}
res <- dsBayesPathAnalysisClient::ds.hessSEM("R", "na_sem_data.txt", 200, 1, 0, 1)
```
### Output results for na_sem_data.txt
```{r}
print(res)
```
### Log out of Opal
```{r}
DSI::datashield.logout(conns)
```
